KPIs and Visualisations

### 2022-07-23 Report/KPIs and Visualisations.Rmd
Copying over chang. Spelling mistake.

>Her har jeg brukt enkle LaTeX mattefunsksjoner for å vise utregningene.

@@

##### KPI_to_string
```{r}
# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable) {
  # Returning NA if the KPI is Inf (division by zero) or NA, to avoid
  # layout-breaking errors, otherwise formatting
  if (is.na(variable)) {
    NA
  } else if (variable == Inf) {
    NA
  } else {
    # Shortening (lengthening) the value, adding %
    str_c(format(variable, digits = 3), "%")
  }
}
```

>>>>

>Her har jeg brukt enkle LaTeX mattefunksjoner for å vise utregningene.

@@

##### KPI_to_string
```{r}
# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable) {
  # Returning NA if the KPI is Inf (division by zero) or NA, to avoid
  # layout-breaking errors, otherwise formatting. (The check for NA is needed to
  # avoid passing an NA to subsequent operations.)
  if (is.na(variable)) {
    NA
  } else if (variable == Inf) {
    NA
  } else {
    # Shortening (lengthening) the value, adding %
    str_c(format(variable, digits = 3), "%")
  }
}
```
